Hypertension and microbiome

### 2019-10-09 articletwo.Rmd
Jitter to boxplot

```{r deseq boxplot}
g.boxplot <- dset.deseq.boxplot %>% 
    ggplot(aes(x=HYPERTENSION, y=Abundance, color = OTU)) +
    geom_boxplot(lwd=0.1, outlier.size = 0.1) +
    scale_y_continuous(limits = c(0, 0.5)) +
    scale_x_discrete(labels=c("0" = "Normotensive", "1" = "Hypertensive")) +
    ylab("Sqrt For Relative Abundances") +
    theme_classic() +
    guides(shape = guide_legend(override.aes = list(size = 0.1)),
           color = guide_legend(override.aes = list(size = 0.1))) +
    theme(legend.title = element_text(size = 4), 
          legend.text  = element_text(size = 4),
          legend.key.size = unit(1, "lines"),
          legend.position="bottom")
ggsave(file = "cache/dds-test.png", plot=g.boxplot, height=7, width=6, units = "in", dpi = 300)
```

>>>>

```{r deseq boxplot}
g.boxplot <- dset.deseq.boxplot %>%
    filter(OTU %in% pull(dset.deseq.signf  %>% dplyr::filter(abs(log2FoldChange) > 1), Feature)) %>%
    group_by(OTU) %>%
    mutate(outlier = abs(Abundance) > median(Abundance) + IQR(Abundance) * 1.5) %>%
    ggplot(aes(x=HYPERTENSION, y=Abundance, color = OTU)) +
    geom_boxplot(lwd=0.1, outlier.shape = NA) +
    geom_point(data = function(x) dplyr::filter_(x, ~ outlier),
               position = position_jitterdodge(jitter.width = 0.2), size = 0.01, alpha = 0.4) +
    scale_y_continuous(limits = c(0, 0.1)) +
    scale_x_discrete(labels=c("0" = "Normotensive", "1" = "Hypertensive")) +
    ylab("Sqrt For Relative Abundances") +
    theme_classic() +
    guides(shape = guide_legend(override.aes = list(size = 0.1)),
           color = guide_legend(override.aes = list(size = 0.1))) +
    theme(legend.title = element_text(size = 4), 
          legend.text  = element_text(size = 4),
          legend.key.size = unit(1, "lines"),
          legend.position="bottom")
ggsave(file = "cache/dds-test.png", plot=g.boxplot, height=4, width=6, units = "in", dpi = 300)
```
